\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-06-09 doc/flexiblesusy-paper.tex
rename paper TeX file

As explained at the beginning of \secref{sec:SpecGenStruct}, the RGEs
plus the user-defined boundary conditions on the model parameters form
a boundary value problem.  \fs provides a default two-scale boundary
value problem solver, which tries to find a set of model parameters
consistent with all constraints at all scales.  It does so by running
iteratively between the scales of all boundary conditions, imposing
the constraints (by calling the corresponding \code{apply()} function)
and checking for convergence after each iteration.  This approach is
described in \cite{Barger:1993gh} for the MSSM and is widely
implemented in SUSY spectrum generators.

In more detail the two-scale algorithm used in \fs works as
follows, see also \figref{fig:two-scale-algorithm}:

>>>>

As explained at the beginning of \secref{sec:SpecGenStruct}, the RGEs
plus the user-defined boundary conditions on the model parameters form
a boundary value problem.  \fs provides a default two-scale boundary
value problem solver, which tries to find a set of model parameters
consistent with all constraints at all scales.  It does so by running
iteratively between the scales of all boundary conditions, imposing
the constraints (by calling the corresponding \code{apply()} function)
and checking for convergence after each iteration.  This approach is
described in \cite{Barger:1993gh} originally for the MSSM and is widely
implemented in SUSY spectrum generators.
Despite sharing the same algorithm with others,
the boundary value problem solver class from \fs, named \code{RGFlow},
has two notable properties.
First, it extends the aforementioned procedure to towers of models.
If the problem involves more than one model,
\code{RGFlow} matches one model to the next after
running the model parameters to the matching scale.
Second, \code{RGFlow} is an abstract implementation of
the algorithm, unaware of physics, in that
it is free of hard-wired model-dependent code related to
RGEs, boundary or matching conditions, or initial guesses.
All these pieces of physics information are
carried by separate objects which one then
links to \code{RGFlow} to set up a boundary value problem.
This modular design makes it easy
to replace any of the above components,
as shall be demonstrated in \secref{sec:integrating-custom-built}.

In more detail the two-scale algorithm used in \fs,
as applied to a problem with a single MSSM-like model,
works as follows, see also \figref{fig:two-scale-algorithm}:
